%-------------------------
% Resume in Latex
% Author : Dmitry Bugakov
% Based on: Wilmer Gonzalez repo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
    \vspace{1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands

\newcommand{\sepsection}{\vspace{25pt}}

\newcommand{\resumeItem}[1]{%2
    \item\small{
    %\textbf{#1}
        #1
    %{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{8pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}     & #2                 \\
        \textnormal{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{5pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textnormal{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeProjectDescription}[2]{\vspace{5pt} \textnormal{#1:} \textit{\small#2}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
\underline{#1:} #2
}

% COLOR THEMES SELECTION

% For Light theme un-comment this and comment the Dark theme section below
% \colorlet{textcolor}{black}
% \colorlet{urlcolor}{blue}

% \begin{document}
% ---

% For Dark theme un-comment this and comment the Light theme section above
\colorlet{textcolor}{white!80!gray}
\colorlet{backgroundcolor}{black!30!gray}
\colorlet{urlcolor}{blue!25!white}
\AtBeginDocument{\color{textcolor}}

\begin{document}
\pagecolor{backgroundcolor}
% ---


% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Dmitry Bugakov} & \textnormal{Email:} \href{mailto:dmitrybugakovdev@gmail.com}{dmitrybugakovdev@gmail.com}\\
\textnormal{Senior Data Engineer \textbar Technical lead} & \href{https://www.linkedin.com/in/dmitrybugakov/}{ \color{urlcolor}{\faicon{linkedin}} \color{textcolor} LinkedIn} \\
\textnormal{Berlin, Germany.} & \href{https://github.com/dmitrybugakov}{ \color{urlcolor}{\faicon{github}} \color{textcolor} GitHub}\\
\end{tabular*}
\vspace{1em}
% ---

% ABOUT ME
\section{About me}

\textnormal{Data Engineer \textbar Architect with a Computer Science degree and over 10 years of experience in designing data-focused solutions. This includes creating data pipelines, analytical tools, data lakes, and warehouses. I have a keen interest in OpenSource projects and am driven by a passion for leveraging technology to better our world.}


\resumeItemListStart
\resumeItem{Strong understanding and hands-on experience with Big Data tools such as Hadoop, Spark, and Airflow, along with high-capacity and resilient systems.}
\resumeItem{Well-versed in cloud platforms like AWS and GCP.}
\resumeItem{Have built streaming solutions using tools such as Kinesis, Kafka, and Pub/Sub combined with Spark streaming.}
\resumeItem{Proficient in developing data-centric architectures, ensuring data governance, and maintaining data quality.}
\resumeItem{Skilled in navigating SDLC processes, upholding code quality standards, and implementing CI/CD processes with monitoring pipelines.}
\resumeItem{Familiar with DataOps and MLOps methods.}
\resumeItem{Good at designing systems, starting new projects, and building prototypes.}
\resumeItem{Conducted over 100 technical interviews as part of hiring processes.}
\resumeItemListEnd

% ---
\vspace{1em}


% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart

% --- Deutsche Bank --- START
\resumeSubheading
{Deutsche Bank \href{www.db.com/}{\color{urlcolor}\faicon{link}}}{Berlin, Germany}
{Senior Data Engineer \textbar Technical lead}{August 2021 - now}

\resumeProjectDescription{Project}{Crafted a Data Platform and Data Lake tailored for BI, ensuring swift access to marts with minimal latency.}

\resumeItemListStart
\resumeItem{Led the revamp of the data platform, minimizing legacy components and transitioning over 100 pipelines to contemporary methodologies.}
\resumeItem{Enhanced development processes by integrating Agile methodologies and fortifying CI/CD pipelines, resulting in heightened productivity and expedited deployment.}
\resumeItem{Oversaw SRE and SL3 practices to ensure reliability and optimal performance.}
\resumeItemListEnd
\resumeTech{Technologies}{Java, Scala, Python, Maven, Hadoop, Clickhouse, Akka, Apache Spark, Pandas, Jupyter, Tableau, Bitbucket, TeamCity etc.}\\
% --- Deutsche Bank --- END

\sepsection

% --- Grid Dynamics --- START
\resumeSubheading
{Grid Dynamics \href{https://www.griddynamics.com/}{\color{urlcolor}\faicon{link}}}{Saint Petersburg, Russian Federation}
{Staff Data Engineer \textbar Technical lead}{November 2020 - June 2021}

\resumeProjectDescription{Project}{Vontier - Developed a combined Data and Data Science platform for enhanced data analysis and model management.}
\resumeItemListStart
\resumeItem{Architected data platform solutions, ensuring optimal performance and scalability.}
\resumeItem{Directed data engineering initiatives, leading innovations and ensuring best practices.}
\resumeItem{Implemented MLOps and streamlined CI/CD processes, along with A/B test monitoring.}
\resumeItemListEnd
\resumeTech{Technologies}{Python, PySpark, Pandas, Airflow, Scikit learn, Statsmodels, MLflow, AWS(S3, EMR, Redshift, Kinesis, SageMaker, IAM, KMS, Cloudformation), Jenkins, and more.}

\resumeSubSubheading
{Senior Data Engineer \textbar Technical lead}{May 2020 - November 2020}

\resumeProjectDescription{Project}{HelloFresh, Germany - Spearheaded the redesign and migration of Data Platform and Data Lake to accommodate rapid growth during the pandemic.}

\resumeItemListStart
\resumeItem{Architected and executed the data platform, creating an efficient data processing framework.}
\resumeItem{Led the data engineering team, driving innovations and best practices.}
\resumeItem{Streamlined development with Agile methodologies and enhanced CI/CD pipelines, boosting productivity and deployment speed.}
\resumeItemListEnd
\resumeTech{Technologies}{Python, Scala, Spark, Deequ, AWS suite (including EMR, Glue, and Redshift), PostgreSQL, Circleci, Docker, Jira, GitHub, and more.}

\resumeSubSubheading
{Senior Data Engineer \textbar Technical lead}{July 2019 - May 2020}

\resumeProjectDescription{Project}{Kohl’s - Engineered a Data Platform and Data Lake for the prominent American retailer, Kohl's Corp. (Project concluded amidst the pandemic.)}

\resumeItemListStart
\resumeItem{Developed an efficient data processing framework while optimizing GCP interactions to reduce costs.}
\resumeItem{Delivered detailed designs, specifications, and comprehensive documentation.}
\resumeItem{Guided and nurtured team members, emphasizing technical proficiency and fostering a culture of innovation.}
\resumeItemListEnd
\resumeTech{Technologies}{Scala, Python, Cats, Hadoop, Spark, Airflow, Maven, GCP(Dataflow, Dataproc, Pub/Sub, BigQuery), Vault, Protegrity, Pgp, Zeppelin, Jenkins, Docker, Confluence, Jira, Sonar, Gerrit, Git, etc.}\\
% --- Grid Dynamics --- END

\sepsection

% --- PerfectArt --- START
\resumeSubheading
{PerfectArt \href{https://perfectart.ru/}{\color{urlcolor}\faicon{link}}}{Moscow, Russian Federation}
{Senior Data Engineer \textbar Technical lead}{June 2018 - June 2019}

\resumeProjectDescription{Project}{Constructed a Data Platform and Data Lake for DB Schenker, a premier logistics company in Germany.}

\resumeItemListStart
\resumeItem{Actively contributed to the overarching design of the data platform architecture.}
\resumeItem{Engineered and implemented key parts of data ingestion into the platform.}
\resumeItem{Streamlined CI/CD processes and optimized git workflows.}
\resumeItemListEnd
\resumeTech{Technologies}{Scala, Python, Hadoop, Hive LLAP, Spark, Akka, Slick, AWS (EMR, S3), Kafka, Gitlab, Docker, Jira, among others.}\\
% --- PerfectArt --- END

\sepsection

% --- Sberbank --- START
\resumeSubheading
{Sber \href{https://www.sberbank.ru/}{\color{urlcolor}\faicon{link}}}{Moscow, Russian Federation}
{Senior Data Engineer}{July 2016 - May 2018}

\resumeProjectDescription{Factory of Data}{A central Data Lake designed to serve all data-centric projects within the bank, acting as the primary source of truth.}

\resumeItemListStart
\resumeItem{Developed a data processing framework using Apache Spark and Apache Hadoop.}
\resumeItem{Implemented data processing pipelines with the same technologies.}
\resumeItem{Managed debugging processes, refactored code, and conducted code reviews.}
\resumeItemListEnd
\resumeTech{Technologies}{Scala, Bash, SBT, Spark, Hadoop, Parquet, Hive, Oozie, Confluence, Jira, Git, Jenkins, among others.}\\
% --- Sberbank --- END

\sepsection

% --- AT Consulting --- START
\resumeSubheading
{AT Consulting \href{https://www.at-consulting.ru/}{\color{urlcolor}\faicon{link}}}{Moscow, Russian Federation}
{Data Analytics Engineer}{October 2013 - June 2016}

\resumeProjectDescription{Project}{Established a Data Lake for a leading telecom operator in Russia.}

\resumeItemListStart
\resumeItem{Development of data processing pipelines using distributed computing technologies}
\resumeItem{Performance optimization and stabilization of a system}
\resumeItem{General debugging, bug fixing and refactoring, code reviewing}
\resumeItemListEnd
\resumeTech{Technologies}{Java, SQL, Maven, Hadoop, Mapreduce, Hive, Pig, Sqoop, Oozie, Avro, Orc, Oracle, Jira, CentOS (bash), SVN.}\\
% --- PerfectArt --- END

\resumeSubHeadingListEnd
% ---


% EDUCATION
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Voronezh State University \href{http://www.vsu.ru/en/}{\color{urlcolor}\faicon{link}}}{Voronezh, Russian Federation}
{Bachelor's Degree in Mathematics and Computer science (Grade 4.4)}{2010 - 2014}
\resumeSubHeadingListEnd
% ---

\end{document}
